\LARGE \bf A Pipeline for Assembling Collision and Near-Collision Dashcam Footage Datasets

### 2021-03-31 paper.tex
switched to document class and bib style templates required by ITSC conference

\documentclass[letterpaper, 10 pt, conference]{IEEEconf}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[style=ieee]{biblatex}
\usepackage{tikz}
\usetikzlibrary{positioning,fit,arrows.meta,backgrounds}
\usepackage{amsmath, amssymb, xcolor, tikz, pgfplots, pgfplotstable}

@@

\bibliography{sources}
\begin{document}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\todo{Overall TODO: fix awkward sentences, grammatical issues }
\begin{abstract}

@@

The software pipeline is built from several modular components called executors that each process or handle the data corresponding to a single video before piping the resulting data to the next executor.

\begin{figure}[htpb]
		\centering
    \tikzset{
        module/.style={%
            draw, rounded corners,
            minimum width=#1,
            minimum height=7mm,
            font=\sffamily
            },
        module/.default=2cm,
        >=LaTeX
    }
    \begin{tikzpicture}[
      % This will show the frame around the figure
      show background rectangle]

@@

    \end{tikzpicture}
		\caption{Architecture of the default pipeline}
		\label{fig:obj-by-class}
\end{figure}

@@

\begin{itemize}
  %\item "collision\_type" contains the type of collision in the video (e.g. car vs. car)
  \item "\texttt{description}": Description of the video as scraped from the video hosting website
  \item "\texttt{state}": String that describes the current state of the video. One of \textit{processed}, \textit{in-progress}, \textit{NULL}
  \item "\texttt{download\_src}": The site that the video was sourced from (e.g. YouTube)
  \item "\texttt{tags}": Object that contains custom user-defined tags on videos and additional data that is site specific
  \item "\texttt{title}": String that represents the type of the video
  \item "\texttt{url}": Url that the video was fetched from
  \item "\texttt{is\_split\_url}": Boolean that is true if all of the frames of the video are covered in this metadata item and false if no
  \item "\texttt{enum\_tags}": List of tags identifying the content of the video. New tags can be added while labelling and can identify anything important in the video.
  \item "\texttt{start\_i}": The start frame of the video that the bounding boxes are created for (if is\_split\_url is true)
  \item "\texttt{end\_i}": The end frame of the video the bounding boxes are created for (if is\_split\_url is true)
  \item "\texttt{bb\_fields}": All bounding-box specific data
  \begin{itemize}
    \item "\texttt{collision\_locations}": List of frame numbers indicating the collision start frames
    \item "\texttt{resolution}": List with 2 elements (Width,Height) representing the resolution of the video the bounding boxes were created for in number of pixels 
    \item "\texttt{objects}": List of all of the bounding boxes for each object in the video. An object being either a vehicle or pedestrian. Within each object, there is metadata specific to that object.
    \begin{itemize}
      \item "\texttt{id}": Unique numerical identifier that represents this object
      \item "\texttt{bboxes}": List of bounding boxes for this specific object. Each bounding box is represented as a 1x5 array with elements (frame number, x1, y1, x2, y2)
      \item "\texttt{class}": The class of the object, such as "car", "pedestrian"
      \item "\texttt{has\_collision}": Boolean that is true if the object is in a collision, false otherwise
    \end{itemize}
  \end{itemize}
\end{itemize}

\begin{figure}
  \begin{lstlisting}[language=json]
{
  "description":"",
  "download_src":"YouTube",
  "tags": {
    "reddit_post_info":{
      "id":"<post_id>"
      "title":"title"
    }
  },
  "title":"Title of the Video",
  "url":"http://www.myvideo.com",
  "is_split_url": false,
  "enum_tags": ["NoCollision"],
  "start_i": 0,
  "end_i": 60,
  "bb_fields": {
    "collision_locations": [],
    "objects": [
      {
        "bboxes": [
          [0, 1096, 377, 1279, 634]
        ],
        "class": "car",
        "has_collision": false,
        "id": "1"
      }
    ],
    "resolution": [1280, 720]
  }
}
  \end{lstlisting}
    \caption{Example Metadata Produced by the Pipeline}
    \label{metadata_example}
\end{figure}

@@

\begin{figure}[htpb]
		\centering
    \begin{tikzpicture}
    \begin{axis}[
      title={Objects by class},
      ylabel={Frequency (\# of objects)},
      xtick=data,
      xticklabels from table={\byclass}{X},
      xticklabel style={rotate=90}
    ]
    \addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byclass;
    \end{axis}
    \end{tikzpicture}
		\caption{Objects grouped by class}
		\label{fig:obj-by-class}
\end{figure}

\begin{figure}[htpb]
		\centering
    \begin{tikzpicture}
    \begin{axis}[
      title={Videos by participant},
      xlabel={Number of participants},
      ylabel={Frequency (\# of videos)},
      xtick=data,
      xticklabels from table={\byactors}{X},
      xticklabel style={rotate=90}
    ]
    \addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byactors;
    \end{axis}
    \end{tikzpicture}
		\caption{Videos grouped by number of participants}
		\label{fig:vids-by-participant}
\end{figure}

\begin{figure}[htpb]
		\centering
    \begin{tikzpicture}
    \begin{axis}[
      title={Videos by agents},
      xlabel={Number of agents},
      ylabel={Frequency (\# of videos)},
      xtick=data,
      xticklabels from table={\byagents}{X}
    ]
    \addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byagents;
    \end{axis}
    \end{tikzpicture}
		\caption{Videos grouped by number of agents}
		\label{fig:vids-by-agents}
\end{figure}

\begin{figure}[htpb]
		\centering
    \begin{tikzpicture}
    \begin{axis}[
      title={Videos by duration},
      xlabel={Duration (in frames)},
      ylabel={Frequency (\# of videos)},
      xtick=data,
      xticklabels from table={\byduration}{X},
      xticklabel style={rotate=90}
    ]
    \addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byduration;
    \end{axis}
    \end{tikzpicture}
		\caption{Videos grouped by duration}
		\label{fig:vids-by-duration}
\end{figure}

\begin{figure}[htpb]
		\centering
    \includegraphics[width=3in]{by-collision.png}
		\caption{Videos by collision}
		\label{fig:vids-by-collision}
\end{figure}

\begin{figure}[htpb]
		\centering
    \includegraphics[width=3in]{by-camera.png}
		\caption{Videos by camera}
		\label{fig:vids-by-camera}
\end{figure}

\todo{Explain the "other" category in the class histogram. These are stationary/non-vehicular objects.}
\todo{Add a paragraph explaining the key characteristics of Figures 5-10.}

@@

\nocite{*}
\printbibliography

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%2345678901234567890123456789012345678901234567890123456789012345678901234567890
%        1         2         3         4         5         6         7         8

\documentclass[letterpaper, 10 pt, conference]{ieeeconf}
\overrideIEEEmargins												% Needed to meet printer requirements.
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{tikz}
\usetikzlibrary{positioning,fit,arrows.meta,backgrounds}
\usepackage{amsmath, amssymb, xcolor, tikz, pgfplots, pgfplotstable}

@@

\begin{document}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\todo{Overall TODO: fix awkward sentences, grammatical issues. }
\begin{abstract}

@@

The software pipeline is built from several modular components called executors that each process or handle the data corresponding to a single video before piping the resulting data to the next executor. Figure \ref{fig:pr_curve} illustrates the organization of the pipeline in its default configuration.

\begin{figure}[htpb]
	\centering
    \tikzset{
        module/.style={%
            draw, rounded corners,
            minimum width=#1,
            minimum height=7mm,
            font=\sffamily
            },
        module/.default=1cm,
        >=LaTeX
    }
    \begin{tikzpicture}[
      % This will show the frame around the figure
      show background rectangle]

@@

    \end{tikzpicture}
		\caption{Architecture of the pipeline in its default configuration. Each node in the diagram represents a stage of the pipeline, consisting of a single executor or series of executors.}
		\label{fig:pipeline-architecture}
\end{figure}

@@

\begin{itemize}
  %\item "collision\_type" contains the type of collision in the video (e.g. car vs. car)
  \item "\texttt{}": Description of the video as scraped from the video hosting website
  \item "\texttt{state}": String that describes the current state of the video. One of \textit{processed}, \textit{in-progress}, \textit{NULL}
  \item "\texttt{download\_src}": The site that the video was sourced from (e.g. YouTube)
  \item "\texttt{tags}": Object that contains custom user-defined tags on videos and additional data that is site specific
  \item "\texttt{title}": String that represents the type of the video
  \item "\texttt{url}": Url that the video was fetched from
  \item "\texttt{is\_split\_url}": Boolean that is true if all of the frames of the video are covered in this metadata item and false if no
  \item "\texttt{enum\_tags}": List of tags identifying the content of the video. New tags can be added while labelling and can identify anything important in the video.
  \item "\texttt{start\_i}": The start frame of the video that the bounding boxes are created for (if is\_split\_url is true)
  \item "\texttt{end\_i}": The end frame of the video the bounding boxes are created for (if is\_split\_url is true)
  \item "\texttt{bb\_fields}": All bounding-box specific data
  \begin{itemize}
    \item "\texttt{collision\_locations}": List of frame numbers indicating the collision start frames
    \item "\texttt{resolution}": List with 2 elements (Width,Height) representing the resolution of the video the bounding boxes were created for in number of pixels 
    \item "\texttt{objects}": List of all of the bounding boxes for each object in the video. An object being either a vehicle or pedestrian. Within each object, there is metadata specific to that object.
    \begin{itemize}
      \item "\texttt{id}": Unique numerical identifier that represents this object
      \item "\texttt{bboxes}": List of bounding boxes for this specific object. Each bounding box is represented as a 1x5 array with elements (frame number, x1, y1, x2, y2)
      \item "\texttt{class}": The class of the object, such as "car", "pedestrian"
      \item "\texttt{has\_collision}": Boolean that is true if the object is in a collision, false otherwise
    \end{itemize}
  \end{itemize}
\end{itemize}

\begin{figure}
  \begin{lstlisting}[language=json,xleftmargin=5mm]
{
  "description":"",
  "download_src":"YouTube",
  "tags": {
    "reddit_post_info":{
      "id":"<post_id>"
      "title":"title"
    }
  },
  "title":"Title of the Video",
  "url":"http://www.myvideo.com",
  "is_split_url": false,
  "enum_tags": ["NoCollision"],
  "start_i": 0,
  "end_i": 60,
  "bb_fields": {
    "collision_locations": [],
    "objects": [
      {
        "bboxes": [
          [0, 1096, 377, 1279, 634]
        ],
        "class": "car",
        "has_collision": false,
        "id": "1"
      }
    ],
    "resolution": [1280, 720]
  }
}
  \end{lstlisting}
    \caption{Example metadata produced by the pipeline}
    \label{metadata_example}
\end{figure}

@@

\begin{figure}[htpb]
		\centering
    \begin{tikzpicture}
    \begin{axis}[
      title={Objects by class},
      ylabel={Frequency (\# of objects)},
      xtick=data,
      xticklabels from table={\byclass}{X},
      xticklabel style={rotate=90}
    ]
    \addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byclass;
    \end{axis}
    \end{tikzpicture}
		\caption{Videos in dataset grouped by object class}
		\label{fig:obj-by-class}
\end{figure}

\begin{figure}[htpb]
		\centering
    \begin{tikzpicture}
    \begin{axis}[
      title={Videos by participant},
      xlabel={Number of participants},
      ylabel={Frequency (\# of videos)},
      xtick=data,
      xticklabels from table={\byactors}{X},
      xticklabel style={rotate=90}
    ]
    \addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byactors;
    \end{axis}
    \end{tikzpicture}
		\caption{Videos in dataset grouped by number of participants}
		\label{fig:vids-by-participant}
\end{figure}

\begin{figure}[htpb]
		\centering
    \begin{tikzpicture}
    \begin{axis}[
      title={Videos by agents},
      xlabel={Number of agents},
      ylabel={Frequency (\# of videos)},
      xtick=data,
      xticklabels from table={\byagents}{X}
    ]
    \addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byagents;
    \end{axis}
    \end{tikzpicture}
		\caption{Videos in dataset grouped by number of agents}
		\label{fig:vids-by-agents}
\end{figure}

\begin{figure}[htpb]
		\centering
    \begin{tikzpicture}
    \begin{axis}[
      title={Videos by duration},
      xlabel={Duration (in frames)},
      ylabel={Frequency (\# of videos)},
      xtick=data,
      xticklabels from table={\byduration}{X},
      xticklabel style={rotate=90}
    ]
    \addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byduration;
    \end{axis}
    \end{tikzpicture}
		\caption{Videos in dataset grouped by duration}
		\label{fig:vids-by-duration}
\end{figure}

\begin{figure}[htpb]
		\centering
    \includegraphics[width=3in]{by-collision.png}
		\caption{All videos in database grouped by collision type}
		\label{fig:vids-by-collision}
\end{figure}

\begin{figure}[htpb]
		\centering
    \includegraphics[width=3in]{by-camera.png}
		\caption{All videos in database grouped by camera type}
		\label{fig:vids-by-camera}
\end{figure}

\todo{Organize figures better, crop out excess whitespace, resize them and place them within the column of the page.}
\todo{Explain the "other" category in the class histogram. These are stationary/non-vehicular objects.}
\todo{Explain the distinctions between the different types of collisions in the collision chart.}
\todo{Add chart showing videos by source (Figure 11).}
\todo{Move Figures 5-11 to Methodology - Video Collection.}
\todo{Reduce caption size for each figure.}
\todo{Add a paragraph explaining the key characteristics of Figures 5-11.}

@@

\nocite{*}
\bibliographystyle{IEEEtran}
\bibliography{sources}
